Datasheet for 'US-Political-Support

### 2024-03-17 paper/datasheet.qmd
renew the content

---
title: "Datasheet for 'A dataset'"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Datasheet for 'US-Political-Support'"

author: 
  - Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun
thanks: "Code and data are available at: <https://github.com/iloveyz12/US-Political-Support>."

format: pdf
number-sections: true
bibliography: references.bib
---
